Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-05-06 fib2.tex
Minor rewording in the discussion. Moved a citation.

@@

There are several interesting avenues for further research. Applying these methods to more realistic models such as concrete microscopic spin models or models with non-topological features would give direct insight into practical error rates needed for topological quantum memories in non-Abelian systems. Another potential direction is to incorporate tensor network methods for simulating anyons~\cite{Pfeifer2010, Pfeifer2012, Singh2014} to improve the speed and scale of the simulations.

>>>>

\stf{Cite~\cite{Pfeifer2010} for braiding tricks}

@@

There are several interesting avenues for further research. Although it is not completely obvious how to do so, applying these methods to more realistic models such as concrete microscopic spin models or models with non-topological features would give direct insight into practical error rates needed for topological quantum memories in non-Abelian systems. Another potential direction is to incorporate tensor network methods for simulating anyons~\cite{Pfeifer2012, Singh2014} to improve the speed and scale of the simulations.
